\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-14 paper1.tex
finished up the unification section

@@

>>>>

After stitching together control point vectors for time, position, and its derivatives, all information required to have a trajectory plan is now in place.
Since $j(t)$ is piecewise constant, it may be integrated to determine an instantaneous trajectory at any moment in time.
To aid in this, univariate splines are created with time as the independent variable, using the control points as knots.
Position along the path $s(t)$ takes the form of a cubic Hermite spline, constructed using the speed control points $v_{B,x}(t)$ to set the derivatives.
Speed along the path $v_{B,x}(t)$ takes the form of a quadratic Hermite spline, with the acceleration control points $a_{B,x}(t)$ used to set the derivatives at every knot.
Acceleration $a_{B,x}(t)$ is piecewise linear, so lookup is a trivial matter.
The same applies to $j_{B,x}(t)$, which may be implemented with a simple table.

However, the time at which the trajectory plan must be referenced is not always known.
The solution to this problem is known as trajectory tracking, and will be discussed in the next section.

@@

\section{Implementation}

\emph{How much should we say here?}
